Operator evolution from the similarity renormalization group and the Magnus expansion

### 2020-07-07 Notes/Operator_evolution/operator_evolution.tex
Updating operator evolution notes
Most up-to-date files which were recently submitted to PRC.

%
\begin{figure*}[tbh]
	\includegraphics[clip,width=0.67\textwidth]{eta_omega_norms_kvnns_900_901_902_3S1_Wegner_k_magnus_6_ds1,0e-05.pdf}%
	\caption{Frobenius norms of $\eta(s)$ and $\Omega(s)$ from Magnus-evolving the high-cutoff LO potentials in the $^3$S$_1$--$^3$D$_1$ coupled channel: $\Lambda=4$ (black dashed), $9$ (red dash-dotted) and $20$\,fm$^{-1}$ (blue solid) where $G=H_D$ and $k_{\rm max}=6$.}
	\label{fig:eta_omega_norms}
\end{figure*}
%

@@

%
\begin{figure}[t!]
    \includegraphics[clip,width=0.48\textwidth]{deuteron_wave_func_coord_space_kvnns_79_111_222_Wegner1,2.pdf}%
    \caption{Deuteron wave functions in coordinate space for the same three chiral potentials as in Fig.~\ref{fig:universality_test_with_sdt_coeff_Wegner} under band-diagonal SRG transformations with $G=H_D$ and $\lambda=1.2$\,fm$^{-1}$. The solid lines correspond to the S-states, and the dashed lines correspond to the D-states.}
    \label{fig:deuteron_wave_funcs_soft}
\end{figure}
%
\begin{figure}[tbh]
    \includegraphics[clip,width=0.48\textwidth]{deuteron_wave_func_coord_space_kvnns_6_900_901_Wegner1,2.pdf}%
    \caption{Same as Fig.~\ref{fig:deuteron_wave_funcs_soft} but for the high-cutoff LO potentials with $\Lambda=4$ and $9$\,fm$^{-1}$ and AV18, and $\lambda=1.2$\,fm$^{-1}$. The inset plot on the left panel shows the initial wave functions zoomed out on the y-axis up to $r=2$ fm.}
    \label{fig:deuteron_wave_funcs_hard}
\end{figure}
%

@@

%
\begin{figure*}[t!]
	\includegraphics[clip,width=0.85\textwidth]{momentum_projection_contours_q0,30_kvnn_111_3S1.png}%
	\caption{Momentum projection operator $\mel{k}{\ataq}{k'}$ for $q=0.3$\,fm$^{-1}$ under SRG transformations using the RKE N$^4$LO 450 MeV potential, evolving with Wegner ($H_D$) and block-diagonal ($H_{BD}$) generators in the $^3$S$_1$ channel. The SRG flow parameter $\lambda$ is varied for $G = H_D$ evolution and fixed at $\lambda=1$\,fm$^{-1}$ for $G = H_{BD}$ evolution. The decoupling scale for $G = H_{BD}$ is $\LambdaBD$.}
	\label{fig:momentum_projection_contours_q0,30_3S1_RKE}

@@

	\includegraphics[clip,width=0.85\textwidth]{momentum_projection_contours_q3,00_kvnn_111_3S1.png}%
	\caption{Same as Fig.~\ref{fig:momentum_projection_contours_q0,30_3S1_RKE} but for $q=3$\,fm$^{-1}$.}
	\label{fig:momentum_projection_contours_q3,00_3S1_RKE}
\end{figure*}
%

@@

%
\begin{figure*}[tbh]
	\subfloat[]{%
	\includegraphics[clip,width=0.35\textwidth]{deuteron_momentum_distributions_kvnn111.pdf}%
	}
	\quad
	\subfloat[]{%
	\includegraphics[clip,width=0.35\textwidth]{high_energy_state_eps300,0_momentum_distributions_kvnn111.pdf}%
	}
	\caption{Momentum distributions from deuteron (a) and a high-energy state (b) with the RKE N$^4$LO 450 MeV potential. Here, we compare SRG-evolved distributions, $G=H_D$ (red solid), $G=H_{BD}$ at $\LambdaBD=2$\,fm$^{-1}$ (blue dash-dotted), and $G=H_{BD}$ at $\LambdaBD=3$\,fm$^{-1}$ (green dash-dotted) each with $\lambda=1.5$\,fm$^{-1}$, to the initial distribution (black dotted). Also, $\varepsilon \approx 300$ MeV for the high-energy state in (b).}
	\label{fig:momentum_distributions_RKE}
\end{figure*}
%

@@

%
\begin{figure*}[tbh]
	\includegraphics[clip,width=0.85\textwidth]{momentum_projection_integrand_contours_q3,00_kvnn_111.png}%
	\caption{Integrand of $\mel{\psi_d}{\ataq}{\psi_d}$ in momentum space where $\psi_d$ is the deuteron wave function and $q=3$\,fm$^{-1}$. Here, we SRG-evolve the operator and wave function where each successive column indicates further evolution under the Wegner and block-diagonal generators with the RKE N$^4$LO 450 MeV potential. We vary the SRG flow parameter $\lambda$ for Wegner evolution and fix it at $\lambda=1$\,fm$^{-1}$ for block-diagonal evolution. The decoupling scale in the block-diagonal generator is denoted by $\LambdaBD$.}
	\label{fig:momentum_projection_integrand_contours_q3,00_RKE}
\end{figure*}
%
\begin{figure*}[tbh]
	\includegraphics[clip,width=0.85\textwidth]{momentum_projection_integrand_contours_q3,00_kvnn_111_eps300,0.png}%
	\caption{Same as Fig.~\ref{fig:momentum_projection_integrand_contours_q3,00_RKE} but with a high-energy state $\psi_{\varepsilon}$ where $\varepsilon \approx 300$ MeV.}
	\label{fig:momentum_projection_integrand_contours_q3,00_eps300_RKE}
\end{figure*}
%

@@

%
\begin{figure*}[tbh]
	\includegraphics[clip,width=0.85\textwidth]{unitary_transformation_ratios_k0_0,1_kpoints_0,5_1,0_1,5_3,0kvnns_79_111_222_3S1_Wegner.pdf}%
	\caption{Numerical tests of factorization of the unitary transformation  by plotting ratios of $|U(k,q)|$ in the $^3$S$_1$ channel as a function of $q$ for fixed $k=k_0$ in the denominator and several values of $k_i$ in the numerator.
    Plateaus in $q$ indicate factorization $U(k,q) \approx \Klo(k)\Khi(q)$, which is expected for $q\gg\lambda$ (outside shaded box) \emph{and} $k < \lambda$. The unitary transformations are generated in each panel for a different chiral EFT potential, all evolved to $\lambda = 2\,\mbox{fm}^{-1}$ with $G = H_D$.}
	\label{fig:factorization_ratios}
\end{figure*}
%

@@

%
\begin{figure*}[tbh]
	\includegraphics[clip,width=0.75\textwidth]{momentum_projection_ratios_q3,00_3S1_Wegner_kvnns_111_79_6_222.pdf}%
	\caption{Ratio of evolved matrix elements $R[\ataq(k,k)]$ (diagonal) and $R[\ataq(k,0)]$ (full off-diagonal) as defined in \eqref{eq:momentum_proj_matrix_elements_ratio} in the $^3$S$_1$ channel for $q = 3\,\mbox{fm}^{-1}$.
	Three potentials are compared to RKE N$^4$LO after evolution to several values of $\lambda$ with $G = H_D$.
	The dotted lines indicate the value of $|\psi^A_{\infty}(q)|^2 / |\psi^B_{\infty}(q)|^2$.}
	\label{fig:R_ratio_comparison}
\end{figure*}
%

@@

%
\begin{figure*}[tbh]
	\includegraphics[clip,width=0.75\textwidth]{unitary_transformation_contours_kvnns_79_111_222_lamb1,5_Lamb2,0.png}%
	\caption{Matrix elements of $\delta U(k,k')$ with the EMN N$^4$LO 500\,MeV, RKE N$^4$LO 450\,MeV, and Gezerlis \textit{et al.}~N$^2$LO 1\,fm potentials with Wegner and block-diagonal generators in the $^3$S$_1$ channel. Here we set $\lambda=1.5$\,fm$^{-1}$ for band-diagonal evolution, and $\LambdaBD=2$ and $\lambda=1$\,fm$^{-1}$ for block-diagonal evolution.}
	\label{fig:delta_U_default_potentials}
\end{figure*}

@@

\begin{figure*}[tbh]
	\includegraphics[clip,width=0.75\textwidth]{unitary_transformation_contours_kvnns_900_901_902_lamb1,2_Lamb2,0.png}%
    \caption{Matrix elements of $\delta U(k,k')$ with the high-cutoff LO potentials with Wegner and block-diagonal generators in the $^3$S$_1$ channel. Here we set $\lambda=1.2$\,fm$^{-1}$ for band-diagonal evolution, and $\LambdaBD=2$ and $\lambda=1$\,fm$^{-1}$ for block-diagonal evolution.}
	\label{fig:delta_U_high_cutoffs}
\end{figure*}
%

>>>>

%
\begin{figure*}[tbh]
	\includegraphics[clip,width=0.67\textwidth]{eta_omega_norms_kvnns_900_901_902_3S1_Wegner_k_magnus_6_ds1p0e-05.pdf}%
	\caption{Frobenius norms of $\eta(s)$ and $\Omega(s)$ from Magnus-evolving the high-cutoff LO potentials in the $^3$S$_1$--$^3$D$_1$ coupled channel: $\Lambda=4$ (black dashed), $9$ (red dash-dotted) and $20$\,fm$^{-1}$ (blue solid) where $G=H_D$ and $k_{\rm max}=6$.}
	\label{fig:eta_omega_norms}
\end{figure*}
%

@@

%
\begin{figure}[t!]
    \includegraphics[clip,width=0.48\textwidth]{deuteron_wave_func_coord_space_kvnns_79_111_222_Wegner1p2.pdf}%
    \caption{Deuteron wave functions in coordinate space for the same three chiral potentials as in Fig.~\ref{fig:universality_test_with_sdt_coeff_Wegner} under band-diagonal SRG transformations with $G=H_D$ and $\lambda=1.2$\,fm$^{-1}$. The solid lines correspond to the S-states, and the dashed lines correspond to the D-states.}
    \label{fig:deuteron_wave_funcs_soft}
\end{figure}
%
\begin{figure}[tbh]
    \includegraphics[clip,width=0.48\textwidth]{deuteron_wave_func_coord_space_kvnns_6_900_901_Wegner1p2.pdf}%
    \caption{Same as Fig.~\ref{fig:deuteron_wave_funcs_soft} but for the high-cutoff LO potentials with $\Lambda=4$ and $9$\,fm$^{-1}$ and AV18, and $\lambda=1.2$\,fm$^{-1}$. The inset plot on the left panel shows the initial wave functions zoomed out on the y-axis up to $r=2$ fm.}
    \label{fig:deuteron_wave_funcs_hard}
\end{figure}
%

@@

%
\begin{figure*}[t!]
	\includegraphics[clip,width=0.85\textwidth]{momentum_projection_contours_q0p30_kvnn_111_3S1.png}%
	\caption{Momentum projection operator $\mel{k}{\ataq}{k'}$ for $q=0.3$\,fm$^{-1}$ under SRG transformations using the RKE N$^4$LO 450 MeV potential, evolving with Wegner ($H_D$) and block-diagonal ($H_{BD}$) generators in the $^3$S$_1$ channel. The SRG flow parameter $\lambda$ is varied for $G = H_D$ evolution and fixed at $\lambda=1$\,fm$^{-1}$ for $G = H_{BD}$ evolution. The decoupling scale for $G = H_{BD}$ is $\LambdaBD$.}
	\label{fig:momentum_projection_contours_q0,30_3S1_RKE}

@@

	\includegraphics[clip,width=0.85\textwidth]{momentum_projection_contours_q3p00_kvnn_111_3S1.png}%
	\caption{Same as Fig.~\ref{fig:momentum_projection_contours_q0,30_3S1_RKE} but for $q=3$\,fm$^{-1}$.}
	\label{fig:momentum_projection_contours_q3,00_3S1_RKE}
\end{figure*}
%

@@

%
\begin{figure*}[tbh]
	\subfloat[]{%
	\includegraphics[clip,width=0.35\textwidth]{deuteron_momentum_distributions_kvnn111.pdf}%
	}
	\quad
	\subfloat[]{%
	\includegraphics[clip,width=0.35\textwidth]{high_energy_state_eps300p0_momentum_distributions_kvnn111.pdf}%
	}
	\caption{Momentum distributions from deuteron (a) and a high-energy state (b) with the RKE N$^4$LO 450 MeV potential. Here, we compare SRG-evolved distributions, $G=H_D$ (red solid), $G=H_{BD}$ at $\LambdaBD=2$\,fm$^{-1}$ (blue dash-dotted), and $G=H_{BD}$ at $\LambdaBD=3$\,fm$^{-1}$ (green dash-dotted) each with $\lambda=1.5$\,fm$^{-1}$, to the initial distribution (black dotted). Also, $\varepsilon \approx 300$ MeV for the high-energy state in (b).}
	\label{fig:momentum_distributions_RKE}
\end{figure*}
%

@@

%
\begin{figure*}[tbh]
	\includegraphics[clip,width=0.85\textwidth]{momentum_projection_integrand_contours_q3p00_kvnn_111.png}%
	\caption{Integrand of $\mel{\psi_d}{\ataq}{\psi_d}$ in momentum space where $\psi_d$ is the deuteron wave function and $q=3$\,fm$^{-1}$. Here, we SRG-evolve the operator and wave function where each successive column indicates further evolution under the Wegner and block-diagonal generators with the RKE N$^4$LO 450 MeV potential. We vary the SRG flow parameter $\lambda$ for Wegner evolution and fix it at $\lambda=1$\,fm$^{-1}$ for block-diagonal evolution. The decoupling scale in the block-diagonal generator is denoted by $\LambdaBD$.}
	\label{fig:momentum_projection_integrand_contours_q3,00_RKE}
\end{figure*}
%
\begin{figure*}[tbh]
	\includegraphics[clip,width=0.85\textwidth]{momentum_projection_integrand_contours_q3p00_kvnn_111_eps300p0.png}%
	\caption{Same as Fig.~\ref{fig:momentum_projection_integrand_contours_q3,00_RKE} but with a high-energy state $\psi_{\varepsilon}$ where $\varepsilon \approx 300$ MeV.}
	\label{fig:momentum_projection_integrand_contours_q3,00_eps300_RKE}
\end{figure*}
%

@@

%
\begin{figure*}[tbh]
	\includegraphics[clip,width=0.85\textwidth]{unitary_transformation_ratios_k0_0p1_kpoints_0p5_1p0_1p5_3p0kvnns_79_111_222_3S1_Wegner.pdf}%
	\caption{Numerical tests of factorization of the unitary transformation  by plotting ratios of $|U(k,q)|$ in the $^3$S$_1$ channel as a function of $q$ for fixed $k=k_0$ in the denominator and several values of $k_i$ in the numerator.
    Plateaus in $q$ indicate factorization $U(k,q) \approx \Klo(k)\Khi(q)$, which is expected for $q\gg\lambda$ (outside shaded box) \emph{and} $k < \lambda$. The unitary transformations are generated in each panel for a different chiral EFT potential, all evolved to $\lambda = 2\,\mbox{fm}^{-1}$ with $G = H_D$.}
	\label{fig:factorization_ratios}
\end{figure*}
%

@@

%
\begin{figure*}[tbh]
	\includegraphics[clip,width=0.75\textwidth]{momentum_projection_ratios_q3p00_3S1_Wegner_kvnns_111_79_6_222.pdf}%
	\caption{Ratio of evolved matrix elements $R[\ataq(k,k)]$ (diagonal) and $R[\ataq(k,0)]$ (full off-diagonal) as defined in \eqref{eq:momentum_proj_matrix_elements_ratio} in the $^3$S$_1$ channel for $q = 3\,\mbox{fm}^{-1}$.
	Three potentials are compared to RKE N$^4$LO after evolution to several values of $\lambda$ with $G = H_D$.
	The dotted lines indicate the value of $|\psi^A_{\infty}(q)|^2 / |\psi^B_{\infty}(q)|^2$.}
	\label{fig:R_ratio_comparison}
\end{figure*}
%

@@

%
\begin{figure*}[tbh]
	\includegraphics[clip,width=0.75\textwidth]{unitary_transformation_contours_kvnns_79_111_222_lamb1p5_Lamb2p0.png}%
	\caption{Matrix elements of $\delta U(k,k')$ with the EMN N$^4$LO 500\,MeV, RKE N$^4$LO 450\,MeV, and Gezerlis \textit{et al.}~N$^2$LO 1\,fm potentials with Wegner and block-diagonal generators in the $^3$S$_1$ channel. Here we set $\lambda=1.5$\,fm$^{-1}$ for band-diagonal evolution, and $\LambdaBD=2$ and $\lambda=1$\,fm$^{-1}$ for block-diagonal evolution.}
	\label{fig:delta_U_default_potentials}
\end{figure*}

@@

\begin{figure*}[tbh]
	\includegraphics[clip,width=0.75\textwidth]{unitary_transformation_contours_kvnns_900_901_902_lamb1p2_Lamb2p0.png}%
    \caption{Matrix elements of $\delta U(k,k')$ with the high-cutoff LO potentials with Wegner and block-diagonal generators in the $^3$S$_1$ channel. Here we set $\lambda=1.2$\,fm$^{-1}$ for band-diagonal evolution, and $\LambdaBD=2$ and $\lambda=1$\,fm$^{-1}$ for block-diagonal evolution.}
	\label{fig:delta_U_high_cutoffs}
\end{figure*}
%
